# Aggregation and pivoting data: part 1

**Scenario.** Now that you have prepared the data, you can start to create pivot tables to aggregate the data and create some reports. From your conversation with Lucy, you know that she is interested in looking into the yearly sales data broken down by **Countries**, **Product Categories** and **Age Groups**.

Load libraries
```{r results='hide', warning=FALSE}
library(tidyverse)
library(knitr)
library(scales)
library(RColorBrewer)
```
Load data for this lab:
```{r}
my_data <- readRDS("./data/processing/data4week3.rds")
str(my_data)
```

---

## Which year did the company start selling touring bikes?
```{r}
ans_1 <- my_data %>%
    arrange(Date) %>%
    filter(`Sub Category` == 'Touring Bikes') %>%
    select(Date, `Product Category`, `Sub Category`)
kable(ans_1[1:10,])
```
  
**Answer:** 2013

---

## Rank the states for Germany, from the highest to lowest revenue   
    
    
```{r}
my_data %>%
    filter(Country == 'Germany') %>%
    group_by(State) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>%
    ggplot(aes(x = reorder(State, Total), y = Total, fill = State)) +
    geom_bar(stat = "identity", width = .6, show.legend = FALSE) +
    scale_y_continuous(labels = scales::dollar, expand = c(.01, 0)) +
    scale_x_discrete(expand = c(0.01, 0)) +
    coord_flip() +
    labs(title = "Revenue by states", y = NULL, x = NULL) +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

---

## Rank the states for Germany, from the highest to lowest revenue for year 2013


```{r}
my_data %>%
    filter(Country == 'Germany', Year == 2013) %>%
    group_by(State) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>%
    ggplot(aes(x = reorder(State, Total), y = Total, fill = State)) +
    geom_bar(stat = "identity", width = .65, show.legend = FALSE) +
    scale_y_continuous(labels = scales::dollar, expand = c(0.01,0)) +
    scale_x_discrete(expand = c(0.01,0)) +
    coord_flip() +
    labs(title = "Revenue by states", x = NULL, y = NULL) +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

---

## Which frame size sold the most?
   
```{r}
my_data %>%
    filter(`Product Category` == 'Bikes') %>%
    group_by(`Frame Size`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>%
    ggplot(aes(x = reorder(`Frame Size`, Total), y = Total)) +
    geom_bar(stat = "identity", width = .5, fill = "tomato2") +
    scale_y_continuous(labels = scales::dollar, expand = c(0.01, 0)) +
    coord_flip() +
    geom_text(aes(label = paste("$", prettyNum(Total, ","))),
              hjust = 1.1, colour = "black") +
    labs(title = "Revenue by Frame Size", x = "Frame Size", y = NULL) +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

---

## Which age group has the lowest revenue?
   
```{r}
my_data %>%
    group_by(`Age Group`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(Total) %>%
    ggplot(aes(x = reorder(`Age Group`, -Total), y = Total, fill = `Age Group`)) +
    geom_bar(stat = "identity", width = .5, show.legend = FALSE) + 
    scale_y_log10(breaks = c(1e5, 1e6, 1e7, 2e7), expand = c(0.01, 0),
                  limits = c(1e5, 2e7), oob = scales::squish, labels = scales::dollar) +
    scale_x_discrete(expand = c(0.01, 0)) +
    labs(title = "Revenue by Age Group", x = NULL, y = NULL) +
    theme_classic() +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

---  

Now add a chart that shows yearly **Sales** by **Country**. Select a line chart to display the yearly trend. Make sure that the years are located in the X axis, the **Revenue** in the Y axis, and the **Countries** as categories.  
  
In this chart, you can clearly see the sales trend for each **Country**.  
  
Set common theme for line charts:
```{r}
line_theme <- theme_classic() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5),
          panel.grid.major = element_line(colour = "gray"),
          panel.grid.minor = element_line(colour = "gray", size = 0.1),
          legend.title = element_text(face = "bold", colour = "black", size = 12),
          legend.text = element_text(size = 11, color = "black"),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

---

## Which country’s trend is the most different when compared to the other countries?

```{r}
my_data %>%
    group_by(Year, Country) %>%
    summarise(Total = sum(Revenue)) %>%
    ggplot(aes(x = Year, y = Total, color = reorder(Country, -Total))) +
    geom_line(size = 1.2) +
    geom_point(size = 2) +
    scale_y_continuous(breaks = seq(0, 6e6, by = 1e6), labels = scales::dollar,
                       limits = c(0, 6.5e6), expand = c(0, 0)) +
    labs(title = "Yearly Sales by Country", x = NULL, y = NULL, color = NULL) +
    line_theme
```

**Answer:** Australia

---

## Which year does the Bikes category have the least sales?  

```{r}
my_data %>%
    group_by(Year, `Product Category`) %>%
    summarise(Total = sum(Revenue)) %>%
    ggplot(aes(x = Year, y = Total, color = reorder(`Product Category`,- Total))) +
    geom_line(size = 1.2) +
    geom_point(size = 2) +
    scale_y_continuous(limits = c(0, 15e6),labels = scales::dollar, expand = c(0, 0)) +
    labs(title = "Yearly Sales by Category", x = NULL, y = NULL, color = NULL) +
    line_theme
```
  
**Answer:** 2014

---

Add another pivot chart, this time for the pivot table that shows **Revenue** by **Age Group**. Select a pie chart to display the proportion of each **Age Group**. Add the labels to show percentage, formatted to two decimal points.  

```{r ans_3}
ans_3 <- my_data %>%
    group_by(`Age Group`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(Total) %>%
    mutate(Prop = formatC(Total / sum(Total), digits = 4, format = "f") %>%
               as.numeric(),
           Percent = paste(Prop * 100, "%"),
           y_tick = cumsum(Prop) - Prop / 2)

ans_3$`Age Group` <- factor(ans_3$`Age Group`, levels = ans_3$`Age Group`)
kable(ans_3)
```

In this chart, we can clearly see the proportion of sales for each **Age Group**.

## What is the proportion of sales for Young Adults?
```{r}
ggplot(ans_3, aes(x = "", y = Prop, fill = `Age Group`)) +
    geom_bar(width = 1, stat = "identity", colour = "white", size = 0.7) +
    coord_polar(theta = "y") +
    labs(title = "Sales by Age Group", x = NULL, y = NULL) +
    geom_text(aes(x = c(1.6, 1.2, 1.1, 1.1), y = 1 - y_tick, label = Percent), size = 7) +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
          legend.title = element_blank(),
          legend.text = element_text(size = 10, color = "black"),
          axis.text = element_blank(),
          axis.ticks = element_blank()) +
    scale_fill_brewer(palette = "Set1")
```

**Answer:** `r ans_3[ans_3$'Age Group' == "Young Adults", ]$Percent`

---

Add another pivot chart, this time for the pivot table that shows **Revenue** by **Frame size**. Select a bar chart to display the order of sales by **Frame size**. Sort the Y axis to show the **Frame size** that has the most sales on the top.  

```{r ans_4}
ans_4 <- my_data %>%
    filter(!is.na(`Frame Size`)) %>%
    group_by(`Frame Size`) %>%
    summarise(`Total Revenue` = sum(Revenue)) %>%
    arrange(`Total Revenue`)
```

---

## In this chart, you can clearly see the order of sales by frame size. Which frame size sold the least?
```{r}
ggplot(ans_4, aes(x = reorder(`Frame Size`, `Total Revenue`), y = `Total Revenue`)) +
    geom_bar(stat = "identity", width = 0.7, show.legend = FALSE, fill = "tomato2") +
    scale_y_continuous(labels = scales::dollar, expand = c(0.01, 0),
                       limits = c(0, max(ans_4$`Total Revenue`)*1.05)) +
    coord_flip() +
    geom_text(aes(label = paste("$", prettyNum(`Total Revenue`, ","))),
              hjust = 1.1, colour = "black") +
    labs(x = "Frame Size", y = NULL, title = "Sales by Frame Size") +
    theme_classic() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```

**Answer:** 54