# Lab8: Scenario

Upon reviewing the growth report you created, Lucy asked for a report that shows composition of **Product Categories** and **Sub Categories** based on certain filters, including **Year**, **Country**, **Customer Gender**, and **Age Group**.

Specifically, Lucy wants to see the report visualized using a hierarchical chart.

Load necessary libraries
```{r results = "hide"}
library(tidyverse)
library(treemapify)
library(RColorBrewer)
library(knitr)
library(scales)
```
Load data for Lab7
```{r}
my_data <- readRDS("./data/processing/data4week3.rds")
```

---

## Explore the sales composition of bikes category for each age group. Which age group does the composition (rank of sales) differ than the rest?
```{r}
ans_1 <- my_data %>%
    filter(`Product Category` == "Bikes") %>%
    group_by(`Age Group`, `Sub Category`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>% 
    ungroup() 

ans_1 %>%
  mutate_at(vars(Total), funs(scales::comma)) %>% 
  kable()
```
**Show answer on chart:**
```{r}
ggplot(ans_1, aes(area = Total, fill = `Sub Category`, group = `Age Group`, label = `Age Group` )) +
    geom_treemap(colour = "white", size = 2) +
    geom_treemap_text(colour = "black", place = "centre", grow = T, min.size = 3) +
    scale_fill_brewer(palette = "Set2", labels = paste(ans_1$`Sub Category`, '\t')) +
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.text = element_text(size = 14, face = "bold"))
```
**Answer:** `r top_n(ans_1, -1)$'Age Group'` (right upper corner)

---

Now explore the sales composition of Bikes category for each Age Group for the Male customers.
```{r}
ans_2 <- my_data %>%
    filter(`Product Category` == "Bikes", `Customer Gender` == "M") %>%
    group_by(`Age Group`, `Sub Category`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>% 
    ungroup()

ans_2 %>% 
  mutate_at(vars(Total), funs(scales::comma)) %>% 
  kable()
```

---

## Now explore the sales composition of bikes category for each age group, for the Male customers. Which age group does the composition differ than the rest?
```{r}
ggplot(ans_2, aes(area = Total, fill = `Sub Category`, group = `Sub Category`, label = `Age Group` )) +
    geom_treemap(colour = "white", size = 2) +
    geom_treemap_text(colour = "black", place = "centre", grow = T, min.size = 3) +
    scale_fill_brewer(palette = "Set2", labels = paste(ans_2$`Sub Category`, '\t')) +
    theme(legend.position = "top",
          legend.title = element_blank(),
          legend.text = element_text(size = 14, face = "bold"))
```
**Answer 2:** The composition are the same across Age Group for Male customers.

---

## Clear all filters. Now, filter for the year 2016 and Germany. Rank the sales from the highest to lowest for the clothing category
```{r}
ans_3 <- my_data %>%
    filter(Year == 2016, Country == "Germany", `Product Category` == "Clothing") %>%
    group_by(`Sub Category`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>% 
    ungroup()

ans_3 %>% 
  mutate_at(vars(Total), funs(scales::comma)) %>% 
  kable()
```
**Show answer on chart:**
```{r}
ggplot(ans_3, aes(x = reorder(`Sub Category`, -Total), y = Total, fill = `Sub Category`)) +
    geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) +
    labs(x = "Sub Category") +
    scale_y_log10(breaks = c(1, 1e2, 1e3, 1e4, 2e4, 1e5),
                  expand = c(0.02, 0.0), labels = scales::dollar) +
    theme_classic() +
    theme(axis.title = element_text(size = 12, face = "bold"),
          axis.text = element_text(size = 11, colour = "black"))
```

---

## Rank the sales from the highest to lowest for the clothing category. Keep the filter settings and add filter by male customers.

```{r}
ans_4 <- my_data %>%
    filter(Year == 2016, Country == "Germany",
           `Product Category` == "Clothing", `Customer Gender` == "M") %>%
    group_by(`Sub Category`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>% 
    ungroup()

ans_4 %>% 
  mutate_at(vars(Total), funs(scales::comma)) %>% 
  kable()
```
**Show answer on chart:**
```{r}
ggplot(ans_4, aes(x = reorder(`Sub Category`, -Total), y = Total, fill = `Sub Category`)) +
    geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) +
    labs(x = "Sub Category") +
    scale_y_log10(breaks = c(1, 10, 100, 1e3, 5e3, 15e3, 5e4),
                  expand = c(0.02, 0.0), labels = scales::dollar) +
    theme_classic() +
    theme(axis.title = element_text(size = 12, face = "bold"),
          axis.text = element_text(size = 11, colour = "black"))
```

---

## Rank the sales from the highest to lowest for the clothing category. Keep the filter settings and add filter by youth age group
```{r}
ans_5 <- my_data %>%
    filter(Year == 2016, Country == "Germany", `Product Category` == "Clothing",
           `Customer Gender` == "M", `Age Group` == "Youth") %>%
    group_by(`Sub Category`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>% 
    ungroup()

ans_5 %>% 
  mutate_at(vars(Total), funs(scales::comma)) %>% 
  kable()
```
**Show answer on chart:**
```{r}
ggplot(ans_5, aes(x = reorder(`Sub Category`, -Total), y = Total, fill = `Sub Category`)) +
    geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) +
    labs(x = "Sub Category") +
    scale_y_log10(breaks = c(1, 10, 100, 1000, 5000),
                  expand = c(0.02, 0.0), labels = scales::dollar) +
    theme_classic() +
    theme(axis.title = element_text(size = 12, face = "bold"),
          axis.text = element_text(size = 11, colour = "black")
          )
```