
# Lab8: Scenario
Lastly, Lucy wants to have more information about the customer demographics in addition to the already available age and gender. Since your data has **Customer ID** for each row, you can "connect" these rows with your customer demographics database. Your customer demographics is stored in file "Customer_demographics.txt".

Load necessary libraries
```{r}
library(tidyverse)
library(RColorBrewer)
library(scales)
```
Load data for Lab8:
```{r}
my_data <- readRDS("./data/processing/data4week3.rds")
glimpse(my_data)
```
Customer demographics database:
```{r}
add_data <- read.table("./data/raw/Customer_demographics.txt", sep = ",", header = T) %>%
    as_data_frame()
glimpse(add_data)
```

---

## For those customers who bought bikes, what are the top three (bought the most quantity) customer profiles (marital status and number of children)?
```{r ans_1}
ans_1 <- my_data %>%
    select(`Customer ID`, `Order Quantity`, `Product Category`) %>%
    left_join(add_data %>%
                  select(Customer.ID, MaritalStatus, TotalChildren), c("Customer ID" = "Customer.ID")) %>% 
    filter(`Product Category` == "Bikes") %>%
    group_by(MaritalStatus, TotalChildren) %>%
    summarise(`Total Order` = sum(`Order Quantity`)) %>%
    arrange(desc(`Total Order`)) %>% 
    ungroup()
kable(ans_1)
```
```{r}
ggplot(ans_1, aes(x = factor(TotalChildren), y = `Total Order`, fill = factor(MaritalStatus))) +
    geom_bar(stat = "identity", position = position_dodge(0.55), width = 0.5) +
    scale_y_continuous(breaks = seq(0, 7e3, 1e3), expand = c(0.01, 0),
                       limits = c(0, 7e3), oob = scales::squish) +
    labs(x = "Total Children", fill = "Marital\nStatus") +
    theme(plot.title = element_text(face = "bold", size = 14, hjust = 0.3),
          panel.background = element_rect(fill = "white"),
          legend.title = element_text(colour = "black", size = 10, face = "bold"),
          legend.text = element_text(colour = "black", size = 10, face = "bold"),
          legend.position = c(.95, .90),
          legend.background = element_rect(color = "black"),
          axis.line = element_line(colour = "black"),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```
**Answer:**
1. Single without child
2. Married with one child
3. Married with two children

---

Now, replace the **MaritalStatus** and **TotalChildren** fields with the **YearlyIncome** field from the *Customer_demographic table*.

## For those customers who bought bikes, what are the top three (bought the most quantity) income brackets? (Rank from highest to Lowest) 
```{r ans_2}
ans_2 <- my_data %>%
    select(`Customer ID`, `Order Quantity`, `Product Category`) %>%
    left_join(add_data %>%
                  select(Customer.ID, YearlyIncome), c("Customer ID" = "Customer.ID")) %>% 
    filter(`Product Category` == "Bikes") %>%
    group_by(YearlyIncome)%>%
    summarise(`Total Quantity` = sum(`Order Quantity`)) %>%
    arrange(desc(`Total Quantity`)) %>% 
    ungroup()
kable(ans_2)
```
```{r}
`Yearly Income` <- reorder(ans_2$YearlyIncome, -ans_2$`Total Quantity`)
ggplot(ans_2, aes(x = `Yearly Income`, y = `Total Quantity`)) +
    geom_bar(stat = "identity", width = 0.5, fill = "tomato2") +
    scale_y_continuous(breaks = seq(0, 6e3, by = 1e3), expand = c(0.01, 0),
                       limits = c(0, 6e3), oob = scales::squish) +
    scale_x_discrete(expand = c(0.01, 0), labels = paste0("$", prettyNum(`Yearly Income`, big.mark = "'"))) + 
    theme_classic() +
    theme(axis.text.x = element_text(angle = 65, vjust = 1.0, hjust = 1.0),
          axis.text = element_text(size = 11, colour = "black"),
          axis.title = element_text(size = 12, face = "bold"))
```
**Answer:**  
1. $40`000  
2. $60`000  
3. $70`000  

---

Now, remove the **YearlyIncome** field and replace it with the **EnglishEducation** field from the add_data tibble.

## For those customers who bought bikes, what are the top two (bought the most quantity) education levels?
```{r}
ans_3 <- my_data %>%
    select(`Customer ID`, `Order Quantity`, `Product Category`) %>%
    left_join(add_data %>%
                  select(Customer.ID, EnglishEducation), c("Customer ID" = "Customer.ID")) %>% 
    filter(`Product Category` == "Bikes") %>%
    group_by(EnglishEducation)%>%
    summarise(`Total Quantity` = sum(`Order Quantity`)) %>%
    arrange(desc(`Total Quantity`)) %>% 
    ungroup()
kable(ans_3)
```
```{r}
ggplot(ans_3, aes(x = reorder(EnglishEducation, -`Total Quantity`),
                  y = `Total Quantity`, fill = EnglishEducation)) +
    geom_bar(stat = "identity", width = 0.5, show.legend = FALSE) +
    scale_y_continuous(breaks = seq(0, 15e4, by = 2e3), expand = c(0.01, 0)) +
    scale_fill_brewer(palette = "Dark2") +
    theme_classic() +
    theme(axis.title.x = element_blank(),
          axis.text = element_text(size = 13, colour = "black"),
          axis.title = element_text(size = 14, face = "bold"))
```
**Answer:**  
1. Bachelors  
2. Partial College  

---

Lastly, remove the EnglishEducation field from the Rows and replace it with the **HouseOwnerFlag** field from the *Customer_demographics table*. Format the **Sum of Order Quantity** to show as **Percentage of Grand Total** with two decimal places.

## What is the percentage of the customers who bought Bikes and are house owners?
```{r}
ans_4 <- my_data %>%
    select(`Customer ID`, `Order Quantity`, `Product Category`) %>%
    left_join(add_data %>%
                  select(Customer.ID, HouseOwnerFlag), c("Customer ID" = "Customer.ID")) %>% 
    filter(`Product Category` == "Bikes") %>%
    group_by(HouseOwnerFlag) %>%
    summarise(Total = sum(`Order Quantity`)) %>%
    mutate(`Grand Total, %` = formatC(Total / sum(Total) * 100, digits = 2, format = "f") %>%
               as.numeric()) %>%
    arrange(desc(`Grand Total, %`)) %>% 
    ungroup()
kable(ans_4)
```
```{r}
ggplot(ans_4, aes(x = "", y = Total / sum(Total), fill = HouseOwnerFlag)) +
    geom_bar(width = 1, stat = "identity", colour = "white", size = 0.7) +
    coord_polar(theta = "y") +
    labs(fill = "House\nOwner", x = NULL, y = NULL) +
    geom_text(aes(x = c(1.0, 1.1), y = c(0.35, 0.85), label = paste(`Grand Total, %`, "%")), size = 8) +
    scale_fill_brewer(palette = "Set2") +
    theme(panel.background = element_rect(fill = "white", color = "white"),
          plot.title = element_text(face = "bold", size = 16, hjust = 0.6),
          legend.title = element_text(face = "bold", colour = "black", size = 12),
          legend.text = element_text(size = 10, color = "black"),
          axis.text = element_blank(),
          axis.ticks = element_blank())
```
**Answer:** `r top_n(ans_4, 1)$'Grand Total, %'`%