---
title: "DAT205x: Introduction to Data Analysis using R. Lab2"
output: html_notebook
---
# Scenario
While your first attempt to show the company's performance to Lucy was not bad, clearly she has a lot more requirements than what you provided. She wants to know more about the year over year sales, sliced into different categories, sub-categories, and countries. She also wants to see additional information such as customer demographics.

Jack has provided you with a different data source. This time the data has more than one hundred thousand rows.

Before you can create additional reports to Lucy, first you need to prepare the data.
```{r setup , include=FALSE}
knitr::opts_knit$set(root.dir = getwd())
```
Load libraries
```{r}
library(tidyverse)
library(lubridate)
```
Load data for Lab2:
```{r my_data, cache = TRUE, cache.extra = file.info("./week1/data4week2.rds")}
my_data <- readRDS("./week1/data4week2.rds")
```

---

#### **Question 1:** What is the total revenue for all the sales in the United States?
```{r}
my_data %>%
    filter(Country == "United States") %>%
    summarise(`US Revenue` = sum(Revenue)) %>%
    prettyNum(., big.mark = ",") %>%
    paste0("$", .)
```

---

Now, you need to add several columns, derived from existing columns in the data.
First, let's add a **Month** column. Insert a new column to the left of the **Customer ID** column.
```{r results = 'hide'}
my_data <- my_data %>%
    mutate(Month = month(Date)) %>%
    select(Date:Year, Month, everything())
```

#### **Question 2:** What is the total revenue for all the sales in the Month of December?
```{r}
my_data %>% filter(Month == 12) %>%
    summarise(`Total Revenue` = sum(Revenue)) %>%
    prettyNum(., big.mark = ",") %>%
    paste0("$", .)
# TODO: use top_n for filter data; add chart or table
```

---

Next, let's add an "Age Group" column. Insert a new column to the left of the
Customer Gender, and use formula to derive the age group from the Customer Age
column. Let's group the customers based on the following criteria:

* Youth (<25);
* Young Adults (25-34);
* Adults (35-64);
* Seniors (>64)

Define function age_group()
```{r}
age_group <- function(age) {
        if (age < 25) {
            "Youth"
        } else if (age > 24 & age < 35) {
            "Young Adults"
        } else if (age > 34 & age < 65) {
            "Adults"
        } else {
            "Seniors"
        }
}
```
Add an "Age Group" column
```{r results = 'hide'}
my_data <- my_data %>%
    mutate('Age Group' = map_chr(.$`Customer Age`, age_group)) %>%
    select(Date:`Customer Age`, `Age Group`, everything())
```

#### **Question 3:** What is the total revenue for all the sales for Young Adults Age Group?
```{r}
my_data %>%
    filter(`Age Group` == "Young Adults") %>%
    summarise(Total = sum(Revenue)) %>%
    prettyNum(., big.mark = ",") %>%
    paste0("$", .)
# TODO: use top_n for filter data; add chart or table
```

---

Now, let's add a "Frame Size" column. Insert a new column to the left of the
Order Quantity Use formula to derive the frame size of a bicycle from the last
two characters of the Product column, when the Product Category is Bikes.
Otherwise - NA.

```{r results = 'hide'}
my_data <- my_data %>%
    mutate('Frame Size' = ifelse(my_data$`Product Category` == 'Bikes', my_data$Product, NA) %>%
               str_extract("\\d\\d$") %>%
               as.numeric()) %>%
    select(Date:Product, 'Frame Size', everything())
```

#### **Question 4:** What is the total revenue for all the bikes with frame size 62 for the customer age group Seniors?

```{r}
my_data %>%
    filter(`Product Category` == "Bikes",
           `Frame Size` == 62,
           `Age Group` == "Seniors") %>%
    summarise(`Total Revenue` = sum(Revenue)) %>%
    prettyNum(., big.mark = ",") %>%
    paste0("$", .)
# TODO: use top_n for filter data; add chart or table
```

---

Let's add a **Profit** column. Insert a new column to the right of the **Revenue**, and use formula to derive the **Profit** from both the **Revenue** and **Cost** columns. Show the **Total** for the **Profit** column.  
```{r results = 'hide'}
my_data <- my_data %>%
    mutate(Profit = Revenue - Cost)
```

#### **Question 5:** What is the total profit for United States sales in the month of October 2015, for customer age group Adults?
```{r}
my_data %>%
    filter(Country == "United States", Year == 2015, Month == 10, `Age Group` == "Adults") %>%
    summarise(`Total Profit` = sum(Profit)) %>%
    prettyNum(., big.mark = ",") %>%
    paste0("$", .)
```

---

Save data for next lab:
```{r}
saveRDS(my_data, "week2/data4week3.rds")
```