---
title: "Lab4b"
output: html_document
---

# Load necessary libraries
```{r}
library(tidyverse)
library(scales)
```
## Load data for Lab3b
```{r}
my_data <- readRDS("data4week4.rds")
```
Create an additional pivot chart to show Sales by Customer Gender using
Pie chart. Show percentages for each slice of the pie. Overall, it is split
evenly with 51%:49% of Male to Female ratio.
## Question 1: Which Bike's frame size is more popular for each Gender?
Prepare data:
```{r}
ans_1 <- my_data %>%
    filter(!is.na(`Frame Size`)) %>%
    group_by(`Frame Size`, `Customer Gender`) %>%
    summarise(Total = sum(Revenue))
```
Make bar chart:
```{r}
bar_theme <- theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.3),
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(colour = "black", size = 10, face = "bold"),
    legend.text = element_text(colour = "black", size = 10, face = "bold"),
    axis.line = element_line(colour = "black"),
    axis.text = element_text(size = 10, colour = "black"),
    axis.title = element_text(size = 12)
    )

ggplot(ans_1, aes(x = factor(`Frame Size`), y = Total, fill = factor(`Customer Gender`))) +
    geom_bar(stat = "identity", position = position_dodge(0.6), width = 0.5) +
    scale_x_discrete(expand = c(0, 0)) +
    scale_y_continuous(labels = scales::dollar, expand = c(0, 0)) +
    labs(title = "Which Bike's frame size is more popular for each Gender",
         x = "Frame Size", y = "Sales", fill = "Customer\n  Gender") +
    bar_theme
```
What about Customer Gender vs age group? Right now the Sales by Age Group chart
does not differentiate by Gender. Modify this chart to be a Column chart. Show
the Customer Gender side-by-side for each age group. Sort the Age Group
appropriately.
## Question 2: In Australia, which Age Group has more sales revenue to females
## than to males? (Select two that apply)
```{r}
ans_2 <- my_data %>%
    filter(Country == "Australia") %>%
    group_by(`Age Group`, `Customer Gender`) %>%
    summarise(Total = sum(Revenue)) %>%
    mutate(Prop = formatC(Total / sum(Total), digits = 3, format = "f") %>%
               as.numeric(),
           Percent = paste(Prop * 100, "%"))
```
Make chart:
```{r}
my_theme <- theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.3),
    panel.background = element_rect(fill = "white"),
    legend.title = element_text(colour = "black", size = 10),
    legend.text = element_text(colour = "black", size = 10, face = "bold"),
    axis.line = element_line(colour = "black"),
    axis.text.x = element_text(size = 10, colour = "black"),
    axis.text.y = element_blank(),
    axis.title = element_text(size = 12, face = "bold")
    )
ggplot(ans_2, aes(x = `Age Group`, y = Prop, fill = `Customer Gender`)) +
    geom_bar(stat = "identity", position = "dodge", width = 0.9) +
    scale_x_discrete(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0),
                       limits = c(0, max(ans_2$Prop)*1.05)) +
    labs(title = "How does Age Group differentiate by Gender in Australia?",
         y = "Sales, %", fill = "Customer\n  Gender") +
    geom_text(aes(label = Percent),
              vjust = 1.7,
              colour = "black",
              position = position_dodge(0.8)) +
    my_theme
```

