---
title: "DAT205x: Introduction to Data Analysis using R. Lab3a"
output: html_notebook
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    fig.width = 9,
    fig.height = 7)
# hide output
```

# Scenario

Now that you have prepared the data, you can start to create pivot tables to aggregate the data and create some reports. From your conversation with Lucy, you know that she is interested in looking into the yearly sales data broken down by **Countries**, **Product Categories**, and **Age Groups**.

Load libraries
```{r}
library(tidyverse)
library(knitr)
```
Load data for Lab3a
```{r}
my_data <- readRDS("./week2/data4week3.rds")
```

---

#### **Question 1:** Which year did the company start selling Touring Bikes?
```{r}
my_data %>%
    arrange(Date) %>%
    filter(`Sub Category` == 'Touring Bikes') %>%
    summarise(`Which Year` = first(Year)) %>%
    kable(align = 'l')
# TODO: add chart
```

---

#### **Question 2:** Rank the States for Germany, from the highest to lowest revenue

```{r}
my_data %>%
    filter(Country == 'Germany') %>%
    group_by(State) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>%
    mutate(Rank = min_rank(desc(Total))) %>%
    kable(align = 'lcr')
# TODO: add chart
```

---

#### **Question 3:** Rank the States for Germany, from the highest to lowest revenue for year 2013
```{r}
my_data %>%
    filter(Country == 'Germany', Year == 2013) %>%
    group_by(State) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>%
    mutate(Rank = min_rank(desc(Total))) %>%
    kable(align = 'lcr')
# TODO: add chart
```

---

#### **Question 4:** Which frame size sold the most?
```{r}
my_data %>%
    filter(`Product Category` == 'Bikes') %>%
    group_by(`Frame Size`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(desc(Total)) %>%
    mutate(rank = min_rank(desc(Total))) %>%
    kable(align = 'lcr')
# TODO: add chart
```

---

#### **Question 5:** Which Age Group has the lowest revenue?
```{r}
my_data %>%
    group_by(`Age Group`) %>%
    summarise(Total = sum(Revenue)) %>%
    arrange(Total) %>%
    kable(align = 'lr')
# TODO: add chart
```